\documentclass[9pt]{developercv}
\usepackage{multicol}
\setlength{\columnsep}{0mm}
\usepackage{lipsum}  

\begin{document}

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip}
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Jonathan Rodríguez López}}}}
	
	\vspace{6pt}
	
	{\Large Full Stack Developer}
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth}
	\vspace{-\baselineskip}
	
	\icon{Globe}{11}{\href{http://itsjhonalex.is-a.dev}{itsjhonalex.is-a.dev}}\\
    \icon{MapMarker}{11}{Havana, Cuba}\\
	
\end{minipage}
\begin{minipage}[t]{0.27\textwidth}
	\vspace{-\baselineskip}
	
	\icon{Envelope}{11}{\href{mailto:itsjhonalex@gmail.com}{itsjhonalex@gmail.com}}\\	
    \icon{Github}{11}{\href{https://github.com/ItsJhonAlex}{github.com/ItsJhonAlex}}\\   
    
\end{minipage}

\begin{minipage}[t]{0.46\textwidth}
    \cvsect{Summary}
	\vspace{-6pt}
 
    Versatile and passionate developer dedicated to creating innovative solutions, from backend and frontend design to process automation. Experienced in developing scalable and efficient web applications using JavaScript, Python, React, Node.js, and other modern technologies. Interested in exploring the potential of Web3 and contributing to its development. Extensive experience in project management, including roles as Project Manager, accounting and business management, ensuring quality assurance (Q\&A) and process optimization with tools like Odoo and WordPress. Seeking a challenging environment where I can apply my skills and contribute to the growth of ambitious projects.
\end{minipage}
\hfill
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      Java, C\#, Python, JavaScript, TypeScript, HTML, CSS, SQL.  
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Technologies:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
      React, Node.js, Django, Git, Docker, MySQL, Angular, SpringBoot.
    \end{minipage}
    
\end{minipage}

\cvsect{Projects}
\begin{entrylist}
    \entry
		{Python, Discord API}
		{Tatiana Discord AI Bot}
		{github.com/ItsJhonAlex/TatianaBot}
		{As the lead developer of Tatiana, an AI-powered Discord bot, I focused on enriching the chat experience in online communities. I implemented a modular architecture with plugins using Python and the discord.py API, which facilitated the expansion of functionalities and ensured code maintainability. Key features include seamless integration with Discord, implementation of AI algorithms to generate intelligent and contextual responses, a plugin system for easy addition of new features, and automoderation and user management systems to optimize server operation. This project has been successfully implemented in 54 Discord servers, achieving an 80\% user retention rate thanks to the improved chat experience and a 70\% reduction in incident response time thanks to the automoderation system.}

\end{entrylist}

\vspace{-10 pt}
\begin{entrylist}
   
\end{entrylist}

\vspace{-10 pt}
\cvsect{Experience}
\begin{entrylist}
	\entry
        {Dec 2024 – Jan 2025}
		{Developer}
		{SmartBank}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Participated in the development of a decentralized DeFi platform with various tools and games.
            \item Responsible for the creation and implementation of smart contracts for token management and game logic, as well as integration with the user interface (frontend).
        \end{itemize} 
        \texttt{Solidity} \slashsep \texttt{React} \slashsep \texttt{Node.js}}
	\entry
		{Jul 2020 – Aug 2022}
		{Project Manager (PM)}
		{Arklrealmits}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Responsible for the comprehensive project management in a video game creation studio.
            \item  The main goal was to ensure the successful delivery of projects within the established timeframe and budget, meeting quality standards.
        \end{itemize} 
        \texttt{Agile} \slashsep \texttt{Scrum} \slashsep \texttt{Jira} \slashsep \texttt{Trello}}
	\entry
		{Apr 2018 – Jun 2020}
		{Developer}
		{Alphactory}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Participated in the creation of solutions, modules, and websites in WordPress and Odoo for various clients.
            \item The main goal was to create custom solutions that meet the specific needs of each client.
        \end{itemize} 
        \texttt{WordPress} \slashsep \texttt{Odoo} \slashsep \texttt{PHP} \slashsep \texttt{JavaScript}}
        \entry
		{Jul 2020 - Mar 2021}
		{BotDev Developer}
		{Adeptus Studio}
		{\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Responsible for the design, development, and implementation of innovative chatbots using Node.js and Python.
            \item These bots acted as task and project managers, facilitating communication and coordination between clients and studio workers.
        \end{itemize} 
        \texttt{Node.js} \slashsep \texttt{Python} \slashsep \texttt{Discord API}}
\end{entrylist}

\vspace{-10 pt}
	\cvsect{Languages}
    \vspace{-6pt}
    
    \hspace{26mm} \textbf{English} - B1, \textbf{ Spanish} - Native

\end{document}